HO unification from object language to meta language

### 2024-03-21 paper/appendix.tex
gentex

\begin{elpicode}
  kind address type.
  type addr nat -> address.

  typeabbrev (mem A) (list (option A)).

  type get nat -> mem A -> A -> o.
  get z (some Y :: _) Y.
  get (s N) (_ :: L) X :- get N L X.

  type alloc-aux nat -> mem A -> mem A -> o.
  alloc-aux z [] [none] :- !.
  alloc-aux z L L.
  alloc-aux (s N) [] [none | M] :- alloc-aux N [] M.
  alloc-aux (s N) [X | L] [X | M] :- alloc-aux N L M.

  type alloc address -> mem A -> mem A -> o.
  alloc (addr A as Ad) Mem1 Mem2 :- unset? Ad Mem1, 
    alloc-aux A Mem1 Mem2.

  type new-aux mem A -> nat -> mem A -> o.
  new-aux [] z [none].
  new-aux [A | As] (s N) [A | Bs] :- new-aux As N Bs.

  type new mem A -> address -> mem A -> o.
  new Mem1 (addr Ad) Mem2 :- new-aux Mem1 Ad Mem2.

  type set? address -> mem A -> A -> o.
  set? (addr A) Mem Val :- get A Mem Val.

  type unset? address -> mem A -> o.
  unset? Addr Mem :- not (set? Addr Mem _).

  type assign-aux nat -> mem A -> A -> mem A -> o.
  assign-aux z (none :: L) Y (some Y :: L).
  assign-aux (s N) (X :: L) Y (X :: L1) :- assign-aux N L Y L1.

  type assign address -> mem A -> A -> mem A -> o.
  assign (addr A) Mem1 Val Mem2 :- assign-aux A Mem1 Val Mem2.
\end{elpicode}

\section{The object language}

\begin{elpicode}
~\PYG{k+kd}{type} \PYG{n+nf}{(\Eo)} \PYG{k+kt}{ftm -> ftm -> o}~.                           ~($\customlabel{pred:fequal}{\Eo}$)~
fapp A ~\Eo~fapp B :- map ~(\Eo)~ A B.
flam F ~\Eo~flam G :- pi x\ x ~\Eo~x => F x ~\Eo~G x.
fcon C ~\Eo~fcon C.
fuva N ~\Eo~fuva N.
flam F ~\Eo~T :-                                       ~($\customlabel{clause:eta1}{\eta_l}$)~
  pi x\ beta T [x] (R x), x ~\Eo~x => F x ~\Eo~R x.
T ~\Eo~flam F :-                                       ~($\customlabel{clause:eta2}{\eta_r}$)~
  pi x\ beta T [x] (R x), x ~\Eo~x => R x ~\Eo~F x.
fapp [flam X | L] ~\Eo~T :- beta (flam X) L R, R ~\Eo~T. ~($\customlabel{clause:beta1}{\beta_l}$)~
T ~\Eo~fapp [flam X | L] :- beta (flam X) L R, T ~\Eo~R. ~($\customlabel{clause:beta2}{\beta_r}$)~

type beta fm -> list fm -> fm -> o.
beta A [] A.
beta (flam F) [H | L] R :- subst F H B,
  beta B L R. % since F could be x\app[x|_] and H be lam _ 
beta (fapp A) L (fapp X) :- append A L X.
beta (fuva N) L (fapp [fuva N | L]).
beta (fcon H) L (fapp [fcon H | L]).

type subst (fm -> fm) -> fm -> fm -> o.
subst F H B :- napp (F H) B. % since (F H) may generate (app[app _|_])

type napp fm -> fm -> o.
napp (fcon C) (fcon C).
napp (flam F) (flam G) :- pi x\ napp x x => napp (F x) (G x).
napp (fapp[fapp L|M]) R :- !, append L M N, napp (fapp N) R.
napp (fapp[X]) R :- !, napp X R.
napp (fapp A) (fapp B) :- map napp A B.
napp (fuva N) (fuva N).
\end{elpicode}

>>>>

\input{code/mem}
